---
title: "Interactive Maps of nimue counterfactuals"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    horizontal_layout: fill
    theme: bootstrap
---

```{r setup, include=FALSE}
#prepare data

#Load data and summarise, one cf at a time to work around RAM limits
sum_df <- loadCounterfactualData(c("No Vaccines"),
                         group_by = "iso3c")

##For No vaccines we must adjust for potential floating point/rounding errors
#causing a negative deaths averted
sum_df[sum_df$counterfactual == "No Vaccines" & 
       sum_df$averted_deaths_avg < 0 &
       abs(1-sum_df$deaths_avg/sum_df$baseline_deaths_avg) < 10^-5,
     "averted_deaths_avg"] <- 0
sum_df[sum_df$counterfactual == "No Vaccines" & 
       sum_df$averted_infections_avg < 0 &
       abs(1-sum_df$infections_avg/sum_df$baseline_infections_avg) < 10^-5,
     "averted_infections_avg"] <- 0

world_raw <- readRDS(
  "worldsf.Rds"
) 
#file size too large so need to simplify
world <- world_raw %>% 
  ms_simplify()
#this will remove some island countries so for those we will do so without removing shapes
world <- world %>%
  rbind(
    world_raw %>% filter(!iso3c %in% world$iso3c) %>%
    ms_simplify(keep_shapes = T, explode = T) %>%
      ms_dissolve(field = "iso3c",
                  copy_fields = "country",
                  sum_fields = "geometry")
  )

##prepare for use in leaflet
#add vaccine and population data
pops_df <- squire::population %>%
  group_by(iso3c, country) %>%
  summarise(population = sum(n))
#vaccines actually given
vaccines_df <- readRDS(
  "counterfactuals.Rds"
) %>%
  rename(`Baseline Vaccines` = `Baseline (Total Vaccines)`) %>%
  select(iso3c, `Baseline Vaccines`)
#vaccines given in counter factual
assigned_vaccines_df <- readRDS(
  "counterfactuals.Rds"
) %>%
  select(iso3c, unique(sum_df$counterfactual)) %>%
  pivot_longer(unique(sum_df$counterfactual),
               values_to = "Vaccinated People (1 or 2 doses) (Counterfactual)",
               names_to = "counterfactual")
merged_df <- sum_df %>%
  left_join(pops_df) %>%
  left_join(vaccines_df) %>%
  left_join(assigned_vaccines_df)
#merge with world sf
final_df <- world %>%
  right_join(merged_df, by = "iso3c") %>%
  #sort out countries
  mutate(country = if_else(is.na(country.y), country.x, country.y)) %>%
  select(country, counterfactual, deaths_avg, infections_avg, baseline_deaths_avg,
         baseline_infections_avg, averted_deaths_avg, averted_infections_avg, population,
         `Baseline Vaccines`, `Vaccinated People (1 or 2 doses) (Counterfactual)`, geometry) %>%
  rename(Country = country,
         `Counterfactual Deaths` = deaths_avg,
         `Counterfactual Infections` = infections_avg, `Baseline Deaths` = baseline_deaths_avg,
         `Baseline Infections` = baseline_infections_avg,
         `Counterfactual Deaths compared to Baseline` = averted_deaths_avg,
         `Counterfactual Infections compared to Baseline` = averted_infections_avg) %>%
  #expand to get per population/vaccines
  mutate(`Baseline Vaccines` = if_else(`Baseline Vaccines` == 0,
                                       as.numeric(NA),
                                       `Baseline Vaccines`), #set 0 vaccines to NA so that the per vaccine count is NA
         across(c("Counterfactual Deaths",
                  "Counterfactual Infections",
                  "Baseline Deaths",
                  "Baseline Infections",
                  "Counterfactual Deaths compared to Baseline",
                  "Counterfactual Infections compared to Baseline",
                  "Vaccinated People (1 or 2 doses) (Counterfactual)"
         ),
         list(
           "per 10k" = ~.x/(population/10000),
           "per 1k vaccinations" = ~.x/(`Baseline Vaccines`/1000)
         ),
         .names = "{.col} {.fn}"))

#how many bins to aim for?
n <- 8
#how many signficant digits
digits <- 4
```

Deaths {data-navmenu="No Vaccines"}
===================================== 

Column {.tabset}
-----------------------------------------------------------------------

### Total 

```{r}
map11 <- plot_layered_map(final_df, "No Vaccines", "Deaths", "")
map11
```

### per 10k 

```{r}
plot_layered_map(final_df, "No Vaccines", "Deaths", "per 10k")
```

### per 1k vaccinations (one or more dose)

```{r}
plot_layered_map(final_df, "No Vaccines", "Deaths", "per 1k vaccinations")
```

Infections {data-navmenu="No Vaccines"}
===================================== 

Column {.tabset}
-----------------------------------------------------------------------

### Total 

```{r}
plot_layered_map(final_df, "No Vaccines", "Infections", "")
```

### per 10k 

```{r}
plot_layered_map(final_df, "No Vaccines", "Infections", "per 10k")
```

### per 1k vaccinations (one or more dose)

```{r}
plot_layered_map(final_df, "No Vaccines", "Infections", "per 1k vaccinations")
```

About this counter-factual {data-navmenu="No Vaccines"}
===================================== 

This counter-factual assumes that no vaccines are available for any countries.
The comparison to the baseline can be thought of as the number of deaths averted
by the vaccination campaign. As mentioned in the *About* tab, the values here 
probably represent a upper estimate.

Theoretically no countries should have negative deaths averted. The few countries
that do are countries that received few vaccines and have only seen a increase in 
deaths due to floating point precision errors when calculating the difference
between two identical simulations. These countries have been set to 0.

About
=====================================

Column
-------------------------------------

### Background

This [flexdashboard](https://pkgs.rstudio.com/flexdashboard/) displays [leaflet](https://rstudio.github.io/leaflet/)
maps for a counter-factual-based analysis of the impact of the various COVID-19 
vaccines up  to `r date`. Various counter-factuals, e.g. no vaccines, 
distribution based upon country population size etc. are simulated using Imperial
College London's [nimue model](https://mrc-ide.github.io/nimue/). All other epidemic parameters 
for each country are taken from the fits presented [here](https://mrc-ide.github.io/global-lmic-reports/).
The simulated counter-factuals are compared to a simulation generated using these
fits that represent what occured in reality (this is referred to as the baseline).
The maps show the difference in deaths and infections between these two simulations
for each country. Additionally, the individual numbers of deaths and infections
or vaccines assigned (in the counter-factual) can also be plotted using the icon
in the top right hand corner.

Additional maps with adjustments can be plotted by selecting the relevant tab. 
*Per 10k* refers to deaths/infections per 10,000 people in the countries 
populations and  *per 1k vaccinations* is per 1,000 people vaccinated (with 
at least one dose) in that country **in reality**.

### Limitations

As a warning this method assumes that vaccination campaign have no impact on any
non-vaccine interventions (these are represented by changes in the parameter 
*R<sub>t</sub>*).This could be unreasonable as, for example, if less vaccines 
are available for a country then they might stay in a stricter lockdown than in 
they did in reality. This makes the model's value of *R<sub>t</sub>* higher than
it should be, meaning that for the *No Vaccines* counter-factual the deaths 
averted should be viewed as an upper estimate the true deaths averted.

<!-- This is more complicated for the other counter-factuals since some countries will -->
<!-- be receiving more vaccines than they did in reality hence their *R<sub>t</sub>*  -->
<!-- is likely too low as the country may have reduced their non-vaccine  -->
<!-- interventions more than they did in reality. -->

<!-- These models are currently fitted using reported deaths and some of the reported -->
<!-- cases. Hence this is dependent on the quality of the reported data from each -->
<!-- country and is sensitive to under-reporting. -->

These models are fitted to an excess death estimate, taken from [here](https://github.com/TheEconomist/covid-19-the-economist-global-excess-deaths-model), and so are dependant on the quality of these estimates. Please also note that the model uncertainity does not account for uncertainting the excess mortality estimates.

Column
-------------------------------------

### Figure 1

```{r, echo=FALSE, out.height= "400pt", out.width="500pt"}
mapshot(map11 %>% setView(15, 51, zoom = 4), file = 
         "web_page/plot11.pdf",
        cliprect = "viewport",
        vwidth = 800, vheight = 500, delay  = 2, zoom = 0.5)
include_graphics("web_page/plot11.pdf")
```


Column
-------------------------------------

### Usage

```{r, include=FALSE}
#get values used in text
ukDeathsAverted <- final_df %>%
  filter(counterfactual == "No Vaccines", Country == "United Kingdom") %>%
  pull("Counterfactual Deaths compared to Baseline") %>%
  round() %>%
  format(scientific = FALSE)
```


The maps are presented as chloropleths with categorical colouring, a 
countries exact value can be viewed by hovering over it with your mouse.

The comparison of deaths/infections to the baseline is set up so that positive 
values mean an increase in deaths/infections under the selected counter-factual
and a negative value indicates a decrease. For example in the *No Vaccines* 
counter-factual the UK has a value of `r ukDeathsAverted` (total) deaths as can 
be seen in figure 1. This indicates that there would have been `r ukDeathsAverted`
more  deaths if there had been no vaccines in the UK. It is useful to think of 
`r ukDeathsAverted` as the number of deaths averted by the real-life vaccinations.

The map tabs for simulated and baseline deaths just show the total or adjusted death
counts and by definition are positive numbers. These are both presented on the same
colour scale to make comparisons easier.

The map tab for Vaccinated People (1 or 2 doses) show the number of vaccines assigned to that 
country in the selected counter-factual. For *No Vaccines* this is 0. Please note that
*per 1k vaccinations* is the number of vaccinations total (in the baseline) whilst this map plots people vaccinated (in the counter factual).

Some small island nations, e.g. the Maldives, are represented by tiny polygons.
The best way to view these is to mouse over them whilst zoomed out.
