---
title: "Creating the Report"
author: "Greg Barnsley"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(here::here(), "docs", "create_report.html")) })
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

## Parameter Choices

```{r, echo=TRUE, eval=FALSE}
date <- "2021-09-09"
```

Here we set up our parameters to run the report. Whilst `date` is the only one we 
set there are more parameters available such as `excess` which we will set in
the code as our report will make use of the excess mortality fits for the main
body of the report. Also note that for some of these tasks `excess` and `date` 
do nothing in the code, this is just to make sure that the file is using the 
relevant fits/simulations etc.

## Get Model Fits

```{r, echo=TRUE, eval=FALSE}
repo <- "SET THIS TO THE LOCATION OF YOUR VERSION OF THE GLOBAL_LMIC_REPORTS_ORDERLY"
fetch_fit_id <- orderly::orderly_run("fetch_fits",
                                     parameters = list(
                                       date = date,
                                       excess = TRUE,
                                       repo = repo
                                     ), echo = FALSE)
orderly::orderly_commit(fetch_fit_id)
```

This fetches the model fit objects for report. This take all available objects
from the dedicated fitting repo and requires you to have generated your own fits
with that. Alternatively you can use an included set of fits

## Get other data sources

```{r, echo=TRUE, eval=FALSE}
world_map_id <- orderly::orderly_run("world_map", echo = FALSE)
orderly::orderly_commit(world_map_id)

owid_id <- orderly::orderly_run("owid", parameters = list(date = date), echo = FALSE)
orderly::orderly_commit(owid_id)

income_group_id <- orderly::orderly_run("income_group", echo = FALSE)
orderly::orderly_commit(income_group_id)

who_region_id <- orderly::orderly_run("who_region", echo = FALSE)
orderly::orderly_commit(who_region_id)
```

This gets any other data used e.g. Our World in Data. Archive versions of these 
will be provided with the model fits in the interests of reproducbility. All 
other orderly tasks only draw from objects inside the repo.

## Simulate Counterfactuals

```{r, echo=TRUE, eval=FALSE}
run_simulations_id <- orderly::orderly_run("run_simulations",
                                           parameters = list(
                                             date = date,
                                             seed = 100100,
                                             excess = FALSE,
                                             draws = 15
                                           ), echo = FALSE)
orderly::orderly_commit(run_simulations_id)
```

This is one of the slowest parts of the report. As the number of the draws and 
counter-factuals increases the R objects become very large so it is optimised to 
reduce memory usage and not for speed.

## Create interactive world map

```{r, echo=TRUE, eval=FALSE}
interactive_map_id <- orderly::orderly_run("interactive_map",
                                           parameters = list(
                                             date = date,
                                             excess = FALSE
                                           ), echo = FALSE)
orderly::orderly_commit(interactive_map_id)

#copy files across to github pages directory
destination <- file.path(here::here(), "docs")
origin <- file.path(here::here(), "archive", "interactive_map", 
                    interactive_map_id, "web_page")
for(file in list.files(origin)){
  file.copy(file.path(origin, file), file.path(destination, file), overwrite = TRUE)
}
```

This task generates the interactive leaflet map. The one used on the github 
pages for this repository is copied across from the *web_page* sub directory.

## Generate Table for Report

```{r, echo=TRUE, eval=FALSE}
deaths_averted_table_id <- orderly::orderly_run("deaths_averted_table",
                                           parameters = list(
                                             date = date,
                                             excess = FALSE,
                                             seed = 1001000011
                                           ), echo = FALSE)
orderly::orderly_commit(deaths_averted_table_id)
```

This generates a pdf of a table of the counter factual deaths averted.

## Generate Figures for Report

```{r, echo=TRUE, eval=FALSE}
dot_plots_id <- orderly::orderly_run("dot_plots",
                                           parameters = list(
                                             date = date,
                                             excess = FALSE
                                           ), echo = FALSE)
orderly::orderly_commit(dot_plots_id)


global_deaths_averted_plot_id <- orderly::orderly_run("global_deaths_averted_plot",
                                           parameters = list(
                                             date = date,
                                             excess = FALSE,
                                             seed = 1000100
                                           ), echo = FALSE)
orderly::orderly_commit(global_deaths_averted_plot_id)


tile_plots_id <- orderly::orderly_run("tile_plots",
                                           parameters = list(
                                             date = date,
                                             excess = FALSE,
                                             seed = 99199
                                           ), echo = FALSE)
orderly::orderly_commit(tile_plots_id)
```

These tasks all generate *ggplot* objects so that they are easier to modify when
producing the report.

## Compile Main Body of Report

```{r, echo=TRUE, eval=FALSE}
report_main_id <- orderly::orderly_run("report_main",
                                           parameters = list(
                                             date = date,
                                             excess = FALSE
                                           ), echo = FALSE)
orderly::orderly_commit(report_main_id)
```
