---
title: "Creating the Report"
author: "Greg Barnsley"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(here::here(), "docs", "create_report.html")) })
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

## R Packages

```{r, echo=TRUE, eval=FALSE}
#MRC-IDE Packages
devtools::install_github(
  "mrc-ide/squire.page",
  ref = "3fbb97f3e72c4e6bd7f66690a53f7bb59ce5ea0e"
) #should install odin, squire and nimue
devtools::install_github(
  "mrc-ide/drjacoby",
  ref = "476d94f3eb7357f8e2278834c0af04afd772cf69"
)
devtools::install_github(
  "vimc/orderly"
)
#CRAN packages
install.packages("countrycode") #version 1.3.1
install.packages("future") #version 1.24.0
install.packages("dplyr") #version 1.0.8
install.packages("stringr") #version 1.4.0
install.packages("purrr") #version 0.3.4
install.packages("tidyr") #version 1.2.0
install.packages("readr") #version 2.1.2
install.packages("lubridate") #version 1.8.0
install.packages("tibble") #version 3.1.6
install.packages("rlang") #version 1.0.2
install.packages("ggplot2") #version 3.3.5
install.packages("forcats") #version 0.5.1
install.packages("cowplot") #version 1.1.1
install.packages("ggpubr") #version 0.4.0
install.packages("gridExtra") #version 2.3
install.packages("sf") #version 1.0.7
install.packages("qpdf") #version 1.1
```

All packages used in this repository and the versions used to generate the data.
Feel free to skip if you already have these.

## Parameter Choices

```{r, echo=TRUE, eval=FALSE}
orderly_loc <- here::here()
```

## Get Model Fits

The model fits used to generated the data in this repository are stored in the 
*data* directory. The following tasks gather the simulated counterfactuals from
this directory as well as a world map and dataset from Our World In Data used.

```{r, echo=TRUE, eval=FALSE}
gather_data_id <- orderly::orderly_run("gather_data",
                                           parameters = list(
                                             orderly_loc = orderly_loc
                                           ), echo = FALSE)
orderly::orderly_commit(gather_data_id)
gather_simulations_id <- orderly::orderly_run("gather_simulations",
                                           parameters = list(
                                             orderly_loc = orderly_loc,
                                             excess = TRUE
                                           ), echo = FALSE)
orderly::orderly_commit(gather_simulations_id)
gather_simulations_id <- orderly::orderly_run("gather_simulations",
                                           parameters = list(
                                             orderly_loc = orderly_loc,
                                             excess = FALSE
                                           ), echo = FALSE)
orderly::orderly_commit(gather_simulations_id)
```

## Create interactive world map

```{r, echo=TRUE, eval=FALSE}
interactive_map_id <- orderly::orderly_run("interactive_map",
                                           echo = FALSE)
orderly::orderly_commit(interactive_map_id)
#copy files across to github pages directory
destination <- file.path(here::here(), "docs")
origin <- file.path(here::here(), "archive", "interactive_map", 
                    interactive_map_id, "web_page")
for(file in list.files(origin)){
  file.copy(file.path(origin, file), file.path(destination, file), overwrite = TRUE)
}
```

This task generates the interactive leaflet map. The one used on the github 
pages for this repository is copied across from the *web_page* sub directory.

## Generate Table for Report

```{r, echo=TRUE, eval=FALSE}
deaths_averted_table_id <- orderly::orderly_run("deaths_averted_table",
                                           parameters = list(
                                             excess = TRUE,
                                             seed = 1001000011
                                           ), echo = FALSE)
orderly::orderly_commit(deaths_averted_table_id)

#extra task to correctly calculate percentage deaths averted for COVAX and WHO
COVAX_WHO_percentages_id <- orderly::orderly_run("COVAX_WHO_percentages",
                                           parameters = list(
                                             seed = 10010
                                           ), echo = FALSE)
orderly::orderly_commit(COVAX_WHO_percentages_id)
```

This generates a Rds of a table of the counter factual deaths averted.

## Generate Figures for Report

```{r, echo=TRUE, eval=FALSE}
example_deaths_averted_plots_id <- orderly::orderly_run("example_deaths_averted_plots",
                                           parameters = list(
                                             seed = 1000100
                                           ), echo = FALSE)
orderly::orderly_commit(example_deaths_averted_plots_id)

dot_plots_id <- orderly::orderly_run("dot_plots",
                                           parameters = list(
                                             excess = TRUE
                                           ), echo = FALSE)
orderly::orderly_commit(dot_plots_id)

global_deaths_averted_plot_id <- orderly::orderly_run("global_deaths_averted_plot",
                                           parameters = list(
                                             seed = 1000100
                                           ), echo = FALSE)
orderly::orderly_commit(global_deaths_averted_plot_id)

map_plot_id <- orderly::orderly_run("map_plot",parameters = list(
                                             excess = TRUE
                                           ), echo = FALSE)
orderly::orderly_commit(map_plot_id)
```

These tasks all generate *ggplot* objects so that they are easier to modify when
producing the report.

# Outputs

## Compile Plots to Images

```{r, echo=TRUE, eval=FALSE}
compile_plots_id <- orderly::orderly_run("compile_plots",
                                         echo = FALSE)
orderly::orderly_commit(compile_plots_id)
```

Originally a report this now just puts the plots into pngs. All in one task so
that it is simple to modify dimensions etc.

## Numbers for Report

```{r, echo=TRUE, eval=FALSE}
#a dummy task to get around that orderly tasks can't depend on the same type of
#task twice
reported_data_for_comparison_id <- orderly::orderly_run("reported_data_for_comparison")
orderly::orderly_commit(reported_data_for_comparison_id)

generate_numbers_id <- orderly::orderly_run("generate_numbers",
                                         parameters = list(
                                             seed = 8006646
                                           ),
                                         echo = FALSE)
orderly::orderly_commit(generate_numbers_id)
```

Generate any other values needed for the report.

# Supplementry Plots

## Reported data plots

```{r, echo=TRUE, eval=FALSE}
deaths_averted_table_id <- orderly::orderly_run("deaths_averted_table",
                                           parameters = list(
                                             excess = FALSE,
                                             seed = 100101011
                                           ), echo = FALSE)
orderly::orderly_commit(deaths_averted_table_id)
```

Generate deaths averted table.

```{r, echo=TRUE, eval=FALSE}
delta_toy_example_id <- orderly::orderly_run("delta_toy_example",
                                             parameters = list(seed = 10001),
                                             echo = FALSE)
orderly::orderly_commit(delta_toy_example_id)

delta_toy_example_india_id <- orderly::orderly_run("delta_toy_example_india",
                                             parameters = list(seed = 1012),
                                             echo = FALSE)
orderly::orderly_commit(delta_toy_example_india_id)

ifr_toy_example_id <- orderly::orderly_run("ifr_toy_example",
                                             parameters = list(seed = 99),
                                             echo = FALSE)
orderly::orderly_commit(ifr_toy_example_id)
```

Produce model fits for some simulated data to explore the relationship between
immune escape and deaths averted.

```{r, echo=TRUE, eval=FALSE}
compare_excess_reported_id <- orderly::orderly_run("compare_excess_reported",
                                           parameters = list(
                                             seed = 991001
                                           ), echo = FALSE)
orderly::orderly_commit(compare_excess_reported_id)
```

Comparison of deaths averted in excess-mortality fitting and reported deaths.

```{r, echo=TRUE, eval=FALSE}
deaths_averted_hospital_id <- orderly::orderly_run("deaths_averted_hospital",
                                           parameters = list(
                                             seed = 1000100
                                           ), echo = FALSE)
orderly::orderly_commit(deaths_averted_hospital_id)

deaths_averted_hospital_numbers_id <- orderly::orderly_run("deaths_averted_hospital_numbers",
                                           parameters = list(
                                             seed = 160100
                                           ), echo = FALSE)
orderly::orderly_commit(deaths_averted_hospital_numbers_id)
```

A plot looking at deaths averted by reduction in hospital and ICU burden.

```{r, echo=TRUE, eval=FALSE}
compile_plots_si_id <- orderly::orderly_run("compile_plots_si",
                                         echo = FALSE)
orderly::orderly_commit(compile_plots_si_id)
```

Compile some of the figures and tables for the SI.
